---
output:
  rmarkdown::github_document:
    html_preview: no
---

<!--- README.md is generated from README.Rmd. Please edit that file -->

## locationmisc: Classes, widgets, and functions for the Location App

[![lifecycle](https://img.shields.io/badge/Lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/experimental)

```{r, include = FALSE}
devtools::load_all()
```

### Overview

This package provides classes, widgets, and functions for the [Location App](https://github.com/NCC-CNC/location-app).

### Installation

The package is only available from an [online coding repository](https://github.com/NCC-CNC/locationmisc). To install it, use the following R code.

```{r, eval = FALSE}
if (!require(remotes))
  install.packages("remotes")
remotes::install_github("NCC-CNC/locationmisc")
```

### Usage

This package provides the following widgets:

* `sidebar()`: Constructs a widget that forms a sidebar on a `leaflet` map. It contains the following widgets for customizing its appearance:
    * `sidebarTab()` Constructs a widget that forms a tab in a sidebar. This is used to group together widgets (e.g. those specified below and standard `shiny` widgets) that have related functionality (e.g. a side bar tab could contain widgets for controlling the appearance of a `leaflet` map).
* `newSolutionManager()`: Constructs a widget for creating new solutions. It forms a panel that contains -- in addition to standard `shiny` widgets (e.g. a button to generate a new solution) -- the following widgets for setting goals and weights:
* `mapManager()`: Constructs a widget for controlling the overall appearance of a `leaflet` map. It forms a panel that contains -- in addition to standard `shiny` widgets (e.g. a button to hide all solutions) -- the widgets for controlling the appearnace of weights, themes, and solutions.
