---
output:
  rmarkdown::github_document:
    html_preview: no
---

<!--- README.md is generated from README.Rmd. Please edit that file -->

## locationmisc: 'Shiny' widgets for systematic conservation planning

[![lifecycle](https://img.shields.io/badge/Lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/experimental)

```{r, include = FALSE}
devtools::load_all()
```

### Overview

This package provides classes, widgets, and functions for building web applications for systematic conservation planning under the 'Shiny' framework.

### Installation

The package is only available from an [online coding repository](https://github.com/NCC-CNC/locationmisc). To install it, use the following R code.

```{r, eval = FALSE}
if (!require(devtools))
  install.packages("devtools")
devtools::install_github("NCC-CNC/locationmisc")
```

### Usage

This package provides the following widgets:
* `sidebar()`: Constructs a widget that forms a sidebar on a `leaflet` map. It contains the following widgets for customizing its appearance:
  * `sidebarTab()` Constructs a widget that forms a tab in a sidebar. This is used to group together widgets (e.g. those specified below and standard `shiny` widgets) that have related functionality (e.g. a side bar tab could contain widgets for controlling the appearance of a `leaflet` map).
* `newSolutionPanel()`: Constructs a widget for creating new solutions. It forms a panel that contains -- in addition to standard `shiny` widgets (e.g. a button to generate a new solution) -- the following widgets for setting goals and weights:
    * `singleThemeGoal()`: Constructs a widget for controlling the goal for a theme with a single feature.
    * `multiThemeGoal()`: Constructs a widget for controlling the goals for a theme with multiple features.
    * `weightFactor()`: Constructs a widget for controlling the factor for a weight.
* `mapPanel()`: Constructs a widget for controlling the overall appearance of a `leaflet` map. It forms a panel that contains -- in addition to standard `shiny` widgets (e.g. a button to hide all solutions) -- the following widgets:
  * `tableOfContents()`: Constructs a container widget that contains widgets for controlling the appearance of a particular map component (e.g. theme, solution, weight). Critically, the order of these widgets within this widget controls their relative plotting order on the `leaflet` map. It forms a panel containing the following widgets:
    * `singleThemeVisual()`: Constructs a widget for controlling the appearance of a theme with a single feature on a `leaflet` map.
    * `multiThemeVisual()`: Constructs a widget for controlling the appearance of a theme with multiple features on a `leaflet` map.
    * `weightVisual()`: Constructs a widget for controlling the appearance of a weight on a `leaflet` map.
    * `solutionVisual()`: Constructs a widget for controlling the appearance of a solution on a `leaflet` map. It also contains buttons to inspect the statistics describing the performance/area/representation of solutions too.
