---
output:
  rmarkdown::github_document:
    html_preview: no
---

<!--- README.md is generated from README.Rmd. Please edit that file -->

# Where to Work: Interactive systematic conservation planning application

[![lifecycle](https://img.shields.io/badge/Lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html)
[![Docker Status](https://img.shields.io/docker/cloud/build/naturecons/wheretowork?label=Docker%20build)](https://hub.docker.com/r/naturecons/wheretowork)
```{r, include = FALSE}
knitr::opts_chunk$set(fig.path = "man/figures/README-", fig.align = "center")
```

```{r, include = FALSE}
devtools::load_all()
h = 2.75
w = 3.0
ow = "400"
```

The _Where to Work_ application is a decision support tool to help prioritize conservation efforts for the [Nature Conservancy of Canada](https://natureconservancy.ca/en/).

## Usage

The application is [available online](https://ncc.carleton.ca//wheretowork). **Please note that you must use [Google Chrome](https://www.google.com/chrome/) for it to work.**.

## Installation

The application is available as an online service provided by the [Nature Conservancy of Canada](https://natureconservancy.ca/en/). As such, you don't need to install it on your computer to use: just go to [this link and it's ready to go](https://natureconservancy.ca/en/). If you need to run the application on your own computer, then you can run it using [Docker](https://www.docker.com/) or the [R statistical computing environment](https://www.r-project.org/).

### Using Docker

To run the application using this method, you will need to install the [Docker Engine](https://www.docker.com/) software ([see here for instructions](https://docs.docker.com/get-docker/)). After completing this step, you can install the application from the [DockerHub repository](https://hub.docker.com/repository/docker/naturecons/wheretowork). Specifically, please use the following system command to install the latest official version of the application:

```{bash, eval = FALSE}
docker run -dp 3939:3939 --name wheretowork -it naturecons/wheretowork:latest
```

You can then view the application by opening the following link in [Google Chrome](https://www.google.com/chrome/): http://localhost:3939. After you have finished using the application, you can terminate it using the following system command. **Note that if you don't terminate the application once you are finished using it, then it will continue running in the background.**

```{bash, eval = FALSE}
docker rm -f wheretowork
```

Additionally, the latest development version can be installed using the following system command. Please note that while developmental versions may contain additional features not present in the official version, they may also contain defects.

```{bash, eval = FALSE}
docker run -dp 3939:3939 --name wheretowork -it naturecons/wheretowork:devel
```

Similar to the official version, you can access the developmental version of the application by opening the following link in [Google Chrome](https://www.google.com/chrome/): http://localhost:3939. Also note that you should terminate the developmental version of the application once you are finished using it (using the same code above for the official version).

### Using R

To run the application using this method, you will need to install the [R statistical computing environment](https://www.r-project.org/). After completing the installation, you can install the latest official version of the application by using the following R code:

```{r, eval = FALSE}
if (!require(remotes)) install.packages("remotes")
remotes::install_github("NCC-CNC/wheretowork@*release")
```

You can then use the following R code to run the application and automatically open it in your web browser:

```{r, eval = FALSE}
wheretowork::run_app()
```

Additionally, the latest development version can be installed using the following R code. Please note that while developmental versions may contain additional features not present in the official version, they may also contain defects.

```{r, eval = FALSE}
if (!require(remotes)) install.packages("remotes")
remotes::install_github("NCC-CNC/wheretowork")
```

## Deployment

This application can be deployed using a [nginx web server](https://www.nginx.com/). To achieve this, you first need to install and configure the web server ([see here for instructions](https://www.digitalocean.com/community/tutorials/how-to-install-nginx-on-ubuntu-18-04)). After setting up the web server, you need to update the firewall rules to permit access to port 3939. This is because port 3939 is to serve the application:

```{bash, eval = FALSE}
sudo ufw allow 3939/tcp
```


```
  ##
  # wheretowork application
  ##
  location /wheretowork/ {

    proxy_set_header    Host $host;
    proxy_set_header    X-Real-IP $remote_addr;
    proxy_set_header    X-Forwarded-For $proxy_add_x_forwarded_for;
    proxy_set_header    X-Forwarded-Proto $scheme;
    proxy_pass          http://localhost:3939;
    proxy_read_timeout  20d;
    proxy_buffering     off;

    proxy_set_header    Upgrade $http_upgrade;
    proxy_set_header    Connection $connection_upgrade;
    proxy_http_version  1.1;
    proxy_redirect      http://localhost:3939/ $scheme://$host/wheretowork;


  }
```

Next, restart the web server using the following command. This is important so that it will use the updated configuration file:

```{bash, eval = FALSE}
sudo nginx -s reload
```

Finally, enter the command `sudo make prod` to launch the application. The application can now be accessed at `http://mywebsite.com/wheretowork`, where `mywebsite.com` is the domain of your website.


```
http://nature-vm01.carleton.ca:3939
https://ncc.carleton.ca//wheretowork
sudo nginx -s reload
```


## Contributing

The application is a [Shiny web application](https://mastering-shiny.org/) developed using the [R statistical computing environment](https://www.r-project.org/). Specifically, it uses the [`golem` framework](https://thinkr-open.github.io/golem/). This means that the application is effectively an [R package](https://r-pkgs.org/) that contains code for defining and launching the application (see [here](https://engineering-shiny.org/) for more details). The R code files (located in the `./R` directory) are organized the following system of naming conventions:

* `app_*`: Defines the web application:
    * `app_config.R`: Imports configuration settings.
    * `app_global.R`: Initializes the application. It performs a similar to the `global.R` file in typical Shiny applications.
    * `app_server.R`: Defines the (back-end) server-side logic for the application. It performs a similar role to the `server.R` file in typical Shiny applications.
    * `app_ui.R`: Defines the (font-end) user interface for the application. It performs a similar role to the `ui.R` file in typical Shiny applications.
* `server_*`: Defines components used to assemble the server-side logic for the application.
* `ui_`*: Defines functions used to programmatically create HTML elements for the front-end of the application.
* `class_*`: Defines object orientated programming classes used in the back-end of the application. These classes are implemented using [R6 class system](https://r6.r-lib.org/).
* `fct_*`:  Defines R functions used in the back-end of the application. These files contain code used to perform analyses and manipulate the classes.
* `widget_*`:  Defines custom widgets used by the application. These widgets are implemented using the [`htmlwidgets` framework](https://www.htmlwidgets.org/).
* `utils_*`: Defines utility R functions used in the back-end of the application.

## Getting help

If you have any questions about using the _Where to Work_ application or suggestions for improving it, please contact [Dr. Richard Schuster](https://www.richard-schuster.com/) ([richard.schuster@natureconservancy.ca](mailto:richard.schuster@natureconservancy.ca)) or [Prof. Joe Bennett](https://carleton.ca/bennett-lab/lab-members/) ([JosephBennett@cunet.carleton.ca](mailto:mailto:JosephBennett@cunet.carleton.ca)).
