---
output:
  rmarkdown::github_document:
    html_preview: no
---

<!--- README.md is generated from README.Rmd. Please edit that file -->

# Where to Work: Interactive application for systematic conservation planning

[![lifecycle](https://img.shields.io/badge/Lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html)
[![R-CMD-check-Ubuntu](https://img.shields.io/github/workflow/status/NCC-CNC/wheretowork/Ubuntu/master.svg?label=Ubuntu)](https://github.com/NCC-CNC/wheretowork/actions)
[![R-CMD-check-Windows](https://img.shields.io/github/workflow/status/NCC-CNC/wheretowork/Windows/master.svg?label=Windows)](https://github.com/NCC-CNC/wheretowork/actions)
[![R-CMD-check-Mac-OSX](https://img.shields.io/github/workflow/status/NCC-CNC/wheretowork/Mac%20OSX/master.svg?label=Mac%20OSX)](https://github.com/NCC-CNC/wheretowork/actions)
[![Docker Status](https://img.shields.io/docker/cloud/build/naturecons/wheretowork?label=Docker%20build)](https://hub.docker.com/r/naturecons/wheretowork)
[![Coverage Status](https://codecov.io/github/NCC-CNC/wheretowork/coverage.svg?branch=master)](https://codecov.io/github/NCC-CNC/wheretowork?branch=master)
```{r, include = FALSE}
knitr::opts_chunk$set(fig.path = "man/figures/README-", fig.align = "center")
```

```{r, include = FALSE}
devtools::load_all()
h = 2.75
w = 3.0
ow = "400"
```

The _Where to Work_ application is a decision support tool to help prioritize conservation efforts for the [Nature Conservancy of Canada](https://natureconservancy.ca/en/).

## Installation

The latest official version can be installed from [DockerHub](https://hub.docker.com/repository/docker/naturecons/wheretowork). After [installing Docker on your system](https://docs.docker.com/get-docker/), please use the following system command to install the application:

```{bash, eval = FALSE}
docker run -dp 3838:3838 -it naturecons/wheretowork:latest
```

You can then view the application by opening the following link in [Google Chrome](https://www.google.com/chrome/): http://localhost:3838.

Alternatively, the latest development version can be installed using the following system command. Please note that while developmental versions may contain additional features not present in the official version, they may also contain defects.

```{bash, eval = FALSE}
docker run -dp 3838:3838 -it naturecons/wheretowork:devel
```

You can then view the development version of the application -- similar to the official version -- by opening the following link in [Google Chrome](https://www.google.com/chrome/): http://localhost:3838.

## Usage

TODO.

## Contributing

The application is a [Shiny web application](https://shiny.rstudio.com/) developed using the [R statistical computing environment](https://www.r-project.org/). Specifically, it uses the [`golem` framework](https://thinkr-open.github.io/golem/). This means that the application is effectively an [R package](https://r-pkgs.org/) that contains code for defining and launching the application (see [here](https://engineering-shiny.org/) for more details). The R code files (located in the `./R` directory) are organized the following system of naming conventions:

* `app_*`: Defines the web application:
    * `app_config.R`: Imports configuration settings.
    * `app_global.R`: Initializes the application. It performs a similar to the `global.R` file in typical Shiny applications.
    * `app_server.R`: Defines the (back-end) server-side logic for the application. It performs a similar role to the `server.R` file in typical Shiny applications.
    * `app_ui.R`: Defines the (font-end) user interface for the application. It performs a similar role to the `ui.R` file in typical Shiny applications.
* `server_*`: Defines components used to assemble the server-side logic for the application.
* `ui_`*: Defines functions used to programmatically create HTML elements for the front-end of the application.
* `class_*`: Defines object orientated programming classes used in the back-end of the application. These classes are implemented using [R6 class system](https://r6.r-lib.org/).
* `fct_*`:  Defines R functions used in the back-end of the application. These files contain code used to perform analyses and manipulate the classes.
* `widget_*`:  Defines custom widgets used by the application. These widgets are implemented using the [`htmlwidgets` framework](https://www.htmlwidgets.org/).
* `utils_*`: Defines utility R functions used in the back-end of the application.

## Getting help

If you have any questions about using the _Where to Work_ application or suggestions for improving it, please contact [Dr. Richard Schuster](https://www.richard-schuster.com/) ([richard.schuster@natureconservancy.ca](mailto:richard.schuster@natureconservancy.ca)) or [Prof. Joe Bennett](https://carleton.ca/bennett-lab/lab-members/) ([JosephBennett@cunet.carleton.ca](mailto:mailto:JosephBennett@cunet.carleton.ca)).
